\section{Basic Group Theory}
\subsection{Group Axioms}
\begin{definition}{Group axioms}{}
	Let $G = (G, *)$ be a group where $G$ is a set and $*$ the group operation. Then, the following are true:
	\begin{enumerate}
		\item There exists an identity element $1_{G} \in G$ such that $g * 1_{G} = 1_{G} *g = g$ for all $g \in G$.
		\item Every element $g \in G$ has an inverse $g^{-1} \in G$ such that $g * g^{-1} = 1_{G}$
		\item The product elements in $G$ is associative such that for $a, b, c \in G$, $(a * b) * c = a * (b * c)$.
		\item The product of two elements in $G$ is commutative if and only if the group is abelian. (Ie. if a group $G$ is abelian then $g * q = q * g$ for all $g, q \in G$)
	\end{enumerate}
\end{definition}


\begin{example}{$(\mathbb{Z}, +)$}{}
	Let $G = (\mathbb{Z}, +)$ be the group of integers under addition. Then the identity element is $0$ and the inverse of an integer $g \in G$ is $-g$. The group operation is associative since addition is associative. The group is abelian since addition is commutative. This group is called $\mathbb{Z}$.
\end{example}

\begin{definition}{The set of Rational Numbers}{}
	$\displaystyle\mathbb{Q} = \left\{\frac{a}{b} \hspace{0.1cm} | \hspace{0.1cm} a, b \in \mathbb{Z}, b \neq 0\right\}$
\end{definition}

\begin{question}{Group of Rational Numbers}{}
	{Is $H = (\mathbb{Q}, *)$ a group?} Why or why not?
\end{question}

\subsection{Isomorphisms}
\subsubsection{Bijective functions}
\begin{definition}{Bijective Functions}{}
	A bijective function is a function that is both injective and surjective. This means that the function is both one-to-one (ie. $f(x_1) = f(x_2) \Rightarrow x_1 = x_2$) and onto (ie. if $F: X \to Y$ is our function, then for every $y \in Y \hspace{0.1cm}\exists x \in X : F(x)=y$)
\end{definition}

\begin{definition}{Domain, Codomain, and Range}{}
	Let $f: X \to Y$ be a function. Then,
	\begin{itemize}
		\item $X$ is the \textbf{domain}
		\item $Y$ is the \textbf{codomain}
		\item Let $Z = \left\{ y \in Y \hspace{0.1cm} | \hspace{0.1cm} y=f(x) \hspace{0.1cm} \text{for some } x \in X\right\}$. Then, $Z$ is the \textbf{range} of $f$.
	\end{itemize}
\end{definition}

\subsubsection{Isomorphic Groups}
For two groups to isomorphic essentially means for them to be the same while also being different! Let's start with an example before going to a formal defintion. Consider the two groups $\mathbb{Z} = (\mathbb{Z}, +)$ and $10\mathbb{Z} = (10\mathbb{Z}, +)$ where $10\mathbb{Z} = \{\dots, -20, -10, 0 , 10 , 20, \dots\}$ and $\mathbb{Z} = \{\dots, -2, -1, 0, 1, 2, \dots\}$. Now, take a look at the two groups and realize that they're pretty much the exact same except in the names of the elements. Notice that we can create a \textit{bijective} function $\phi:\mathbb{Z} \to 10\mathbb{Z}$ by the map $x\mapsto 10x$. One extremely interesting property of $\phi$ is that it respects the group operation from $\mathbb{Z}$ to $10\mathbb{Z}$:
\begin{equation*}
	\phi(x + y) = \phi(x) + \phi(y)
\end{equation*}
So, we've created a function that simply just re-assigns the elements without actually changing the structure of the group. \\
\begin{definition}{Isomorphisms}{}
	Let $G = (G, \star)$ and $H = (H, \times)$. $G$ is \textbf{isomorphic} to $H$ if, and only if, there exists a \textit{bijective} function $\phi: G \to H$ such that $\forall g_1, g_2\in G$:
	\begin{equation*}
		\phi(g_1 \star g_2) = \phi(g_1) \times \phi(g_2)
	\end{equation*}
	$\phi$ is called an \textbf{isomorphism}. It's important to note that the left hand side uses the group operation of $G$ and the right hand side uses the group operation of $H$. Note that we can rephrase this to say: If there exists an isomorphism from $G$ to $H$ then, $G$ and $H$ are isomorphic, denoted $G \cong H$. \\
\end{definition}

\begin{example}{Integers mod 6 to multaplicative integers mod 7}{} I claim that $\mathbb{Z}/6\mathbb{Z} \cong (\mathbb{Z}/7\mathbb{Z})^{\times}$ where $\mathbb{Z}/6\mathbb{Z}$ is the group of integers modulo 6 under addition and $(\mathbb{Z}/7\mathbb{Z})^{\times}$ is the group of integers modulo 7 under \textbf{multiplication}. In order to prove isomorphism we must find a function $\phi: \mathbb{Z}/6\mathbb{Z} \to (\mathbb{Z}/7\mathbb{Z})^{\times}$ such that $\phi(x + y) = \phi(x)\phi(y)$. The bijection is
	\begin{equation*}
		\phi(a \bmod 6) = 3^{a} \bmod{7}
	\end{equation*}
	We can see this to be bijective by direct proof
	\begin{equation*}
		(3^0, 3^1, 3^2, 3^3, 3^4, 3^5) \equiv (1, 3, 2, 6, 4, 5) \pmod{7}
	\end{equation*}
	Note that it's techincally $3^{0 \bmod 6}$, but since $a \bmod b = a \Leftrightarrow a < b$ it can be omitted here. Now to verify that $\phi$ respects the group operation we must show that
	\begin{equation*}
		\phi(x+y \bmod 6) = \phi(x\bmod 6)\phi(y\bmod 6)
	\end{equation*}
	However, this is just the same as saying that $\displaystyle 3^{a+b\bmod 6} \equiv 3^{a \bmod 6}3^{b \bmod 6} \pmod{7}$ which we know to be true through properties of exponents.
\end{example}

\subsection{Orders}
\begin{definition}{Order of a Group}{} The order of a group $G$ is the the number of elements in $G$, denoted $|G|$. $|G|$ may be finite or infinite. If $G$ is a \textbf{finite group} then $|G| < \infty$.
\end{definition}
\begin{definition}{Order of an Element}{} The order of an element $g \in G$ is the smallest integer $n$ such that $g^{n} = 1_G$, denoted $|g|$. If there is no value of $n$ such that $g^{n} = 1_{G}$ then $|G|=\infty$.
\end{definition}

\begin{example}{Example Orders of Groups}{}
    \begin{itemize}
        \item The order of the group $\mathbb{Z}$ is $|G| = \infty$.
        \item The order of the group $\mathbb{Z}/6\mathbb{Z}$ is $|G| = 6$.
        \item The order of the group $(\mathbb{Z}/7\mathbb{Z})^{\times}$ is $|G| = 6$.
    \end{itemize}
\end{example}

\subsection{Homomorphisms}
\begin{definition}{Homomorphisms}{}
    Let $G = (G, \star)$ and $H = (H, \times)$. A function $\phi: G \to H$ is a \textbf{homomorphism} if, and only if, $\forall g_1, g_2\in G$:
    \begin{equation*}
        \phi(g_1 \star g_2) = \phi(g_1) \times \phi(g_2)
    \end{equation*}
\end{definition}

Now its important to notice the difference between an isomorphism and a homomorphism: an isomorphism is a homomorphism that is also bijective. This makes sense as isomorphism is a stricter sense of equality so it must have stricter rules. Thus, every isomorphism is a homomorphism, but not every homomorphism is an isomorphism. As well, note that a homomorphism does not need to be surjective or injective, it just needs to preseve the group operation. 

\begin{example}{Examples of homomorphisms}{}
    \begin{itemize}
        \item The identity map $G \to G$ is a homomorphism
        \item There exists \textbf{the trivial homomorphism} $\phi: G \to H$ such that $\phi(g) = 1_H$ for all $g \in G$. This is a homomorphism since $\phi(g_1 \star g_2) = 1_H = 1_H \times 1_H = \phi(g_1) \times \phi(g_2)$.
        \item There is homomorphism from $\mathbb{Z}$ to $\mathbb{Z}/100\mathbb{Z}$ given by the rule $x \mapsto x \bmod 100$.
        \item There is a homomorphism from $\mathbb{Z}$ to itself given by $x \mapsto 2x$. Note that this is injective but not surjective but is still a homomorphism.
    \end{itemize}
\end{example}
Before moving on I encourge you to verify for yourself that the last two examples are indeed homomorphisms.

\begin{fact}{Properties of Homomorphisms}{}
Let $\phi$ be a homomorphism from $G$ to $H$. Then,
    \begin{equation*}
        \phi(1_G) = 1_H \hspace{0.1cm} \text{and} \hspace{0.1cm} \phi(g^{-1}) = \phi(g)^{-1}
    \end{equation*}
\end{fact}
\begin{proof}
    To prove the first property, we can use the fact that $1_G$ is the identity element of $G$. Thus, for any $g \in G$, we have:
    \begin{equation*}
        \phi(1_G) = \phi(1_G * 1_G) = \phi(1_G)\phi(1_G) \Rightarrow \phi(1_G)\phi(1_G)^{-1} = \phi(1_G)\phi(1_G)\phi(1_G)^{-1} \Rightarrow \phi(1_G) = 1_H
    \end{equation*}
    Recall that $\phi(g) \in H$ so $\phi(g)\phi(g)^{-1} = 1_H$ for all $g \in G$. To prove the second property, we can start with the first property and build from there:
    \begin{equation*}
        \phi(g * g^{-1}) = \phi(1_G) = 1_H \Rightarrow \phi(g)\phi(g^{-1}) = 1_H \Rightarrow \phi(g)\phi(g^{-1})\phi(g)^{-1} = \phi(g)^{-1} \Rightarrow \phi(g^{-1}) = \phi(g)^{-1}
    \end{equation*}
\end{proof}

\begin{definition}{Kernel of a Homomorphism}{}
    Let $\phi: G \to H$ be a homomorphism. The \textbf{kernel} of $\phi$, denoted $\ker(\phi)$, is the set of all elements in $G$ that map to the identity element in $H$:
    \begin{equation*}
        \ker(\phi) = \{ g \in G \mid \phi(g) = 1_H \}
    \end{equation*}
    $\ker \phi$ is a subgroup of $G$ (at the very least $1_G \in \ker \phi$)
\end{definition}

\begin{example}{Example Kernels}{}
    \begin{itemize}
        \item The kernel of the trivial homomorphism $\phi: G \to H$ by $x \mapsto 1_H$ is the entire group $G$ itself, $\ker(\phi) = G$.
        \item The kernel of the homomorphism $\phi: \mathbb{Z} \to \mathbb{Z}/100\mathbb{Z}$ given by $x \mapsto x \bmod 100$ is the set of all integers that are multiples of 100, $\ker(\phi) = 100\mathbb{Z} = \{\dots, -200, -100, 0, 100, 200, \dots\}$.
        \item The kernel of the homomorphism $\phi: \mathbb{Z} \to \mathbb{Z}$ given by $x \mapsto 2x$ is the set of all integers that are multiples of 0, which is just $\ker(\phi) = \{0\}$.
    \end{itemize}

\end{example}

\begin{question}{Kernel of an Isomorphism}{}
    What is the kernel of an isomorphism and why?
\end{question}

\subsection{Quotient Groups}
The goal of this section is to define groups in the form $G/N$ such as $\mathbb{Z}/100\mathbb{Z}$. First we have to talk about the kernel and one of its important properties. Recall that the kernel of a homomorphism, $\ker \phi$ is defined as 
\begin{equation} \label{eq:1}
    \{g \in G \mid \phi(g) = 1_H\} 
\end{equation}
Also recall that for any homomorphism $\phi: G \to H$ for $G = (G, \star)$ and $H = (H, \times)$
\begin{equation} \label{eq:2}
    \phi(x \star y) = \phi(x) \times \phi(y)
\end{equation}
Now if we combine~\textbf{\ref{eq:1}} and~\textbf{\ref{eq:2}} it should be evident that for any $g \in \ker\phi$ we have the following, 
\begin{equation} \label{eq:3}
    \phi(g \star x) = \phi(g) \times \phi(x) = 1_H \times \phi(x) = \phi(x)
\end{equation}
So, interestingly enough, it seems as if for any $g \in \ker \phi$ our homomorphism can completely ignore it! Now what does this mean for us in our journey to define a quotient group? Well, lets work with a concrete example to start. Consider the integers modulo 100, $\ZZ/100\ZZ$, which we know to be the set
\begin{equation}
    \ZZ/100\ZZ = \{0, 1, 2, 3, \dots, 97, 98, 99\}
\end{equation}
Now, lets try to define this as a quotient group. We'll begin by taking a look at a homomorphism $\phi: \ZZ to \ZZ/100\ZZ$. It should be clear that $\ker \phi = 100\ZZ$ as $\forall g \in 100\ZZ, \hspace{0.1cm} g \bmod 100 = 0$. Now, let $N = 100\ZZ$ and consider the following
\begin{align*}
    N &= \{\dots, -200, -100, 0, 100, 200, \dots\} \\
    N + 1 &= \{\dots, -199, -99, 1, 101, 201, \dots\} \\
    N + 2 &= \{\dots, -198, -98, 2, 102, 202, \dots\} \\
    &\vdots  \\
    N + 97 &= \{\dots, -103, -3, 97, 197, 297, \dots\} \\
    N + 98 &= \{\dots, -102, -2, 98, 198, 298, \dots\} \\
    N + 99 &= \{\dots, -101, -1, 99, 199, 299, \dots\} \\
\end{align*}

Now we can notice that for $n \in [0, 99]$ if we hold $n$ constant then the image of $\phi(N + n)$ is the same and no two values of $n$ produce the same image. Now I put forth the idea that our quotient group, $Q$, can be thought of the set whose elements are the above sets: 
\begin{equation}
    Q = \ZZ/100\ZZ = \{N, N+1, N+2, \dots, N+97, N+98, N+99\}
\end{equation}
This allows us to construct an equivalence relation on $G$ by saying $x \sim_N y \Leftrightarrow \phi(x) = \phi(y)$ and then think of $Q$ as the equivalence classes of $\sim_N$. Regardless of how you decide to view it, most people find it easier to simply choose on element from each set and use that to represent the different sets. For example, 
\begin{equation*}
    \ZZ/2\ZZ = \braces{\braces{\dots, -2, 0, 2, \dots}, \braces{\dots, -3, -1, 1, \dots}} = \braces{0, 1}
\end{equation*}
This idea is analgous to taking each `fiber' and collapsing it onto a single element. So, what does this all mean? In short, if we have a quotient group $Q \cong G/N$ we can construct $Q$ by using the left cosets of $N$ where $N$ is a normal subgroup of $G$. 

\begin{definition}{Normal Subgroup}{}
    Let $G$ be a group. A subgroug $N$ of $G$ is a \textbf{normal subgroup} of $G$ if it is the kernel of some homomorphism. This is denoted as $N \trianglelefteq G$.
\end{definition}

\begin{definition}{Left Cosets}{}
    Consider a group $N$ such that $N$ is a subgroup of $G$. Any get in the form $gN$ is a \textbf{left coset} of $N$. Note that $N$ can be \textit{any} subgroup of $G$.
\end{definition}

So, to put it all together,
\begin{definition}{Quotient Groups}{}
    Let $N \trianglelefteq G$. Then the quotient group $G/N$ will be the group whose elements are the left cosets of $N$. We must also define the product of two elements in $G/N$, or the product of two cosets $C_1, C_2 \in G/N$. 
    \begin{itemize}
        \item If $c_1$ is the value associated with $C_1$ and $c_2$ is the value associated with $C_2$ then the product $C_1C_2$ will be the coset that contains $c_1c_2$
        \item We can also defing $C_1C_2$ through the representations of $C_1$ and $C_2$. By definition of cosets we know that 
        \begin{equation*}
            C_1 = g_1N \hspace{0.2in} \text{and} \hspace{0.2in} C_2 = g_2N
        \end{equation*}
        for $g_1, g_2 \in G$. Thus, by the same logic above, $C_1C_2$ contains is the coset that contains $g_1g_2$. This definition is equivalent to the one above since $\phi\left(g_1g_2\right) = \phi\left(g_1\right)\phi\left(g_2\right) = c_1c_2$. So, its important to note how we can define this product both in terms of elements in $G$ as well as elements in $H$.
    \end{itemize}
\end{definition}