\addcontentsline{toc}{subsection}{Limit-to-Integral and Integral-to-Limit}
\subsection*{Limit to Integral and Integral to Limit}
This section is to be completed after finishing Unit 5: Sequences and Series. The skills required to be fluent in this section will be strengthened in that unit immensely. In my personal opinion, it would be too many unrelated skills to be able to master amongst all the other content this unit holds.

There will be a standalone assessment on this topic at some point after the conclusion of Unit 5. The module involving this topic will be unlocked but not expected to be completed for quite some time.

\begin{center}
    \hspace{0pt}
    \vfill
    \textbf{Link to Notes}
    \vspace{.7cm}
    
    \qrcode{https://drive.google.com/file/d/1NBu7JxlZUY0V1fztLIygu6aRVqlerBnX/view?usp=sharing}    
    \vfill
    \hspace{0pt}
\end{center}

\newpage

\begin{tcolorbox}[title= DEFINITION OF THE DEFINITE INTEGRAL,colframe=black,sharp corners,colback=white,colbacktitle=white,coltitle=black,boxrule=1pt]

     \textbf{Formal:} If $y=f(x)$ is nonnegative and integrable over a closed interval $[a,\,b]$, then the area under the curve of $y=f(x)$ from $a$ to $b$ is the integral of $f$ from $a$ to $b$,
     \[A=\int_a^b f(x)\,dx\]
     
     \textbf{Informal:} The integral is the NET area between the curve and the $x$-axis. Parts of the area above the curve are positive and parts below the curve are negative.
    
\end{tcolorbox}

\begin{questions}
    \question Evaluate $\displaystyle\int_0^{5\pi/2}\sin x\,dx$.
    \vspace{\stretch{1}}
    
    For the following, evaluate the definite integral and find the TOTAL area between the curve and the $x$-axis.
    \question $\displaystyle\int_2^{\pi+2}\sin(x-2)\,dx$
    \vspace{\stretch{1}}
    
    \question Evaluate the integral $\displaystyle\int_{-2}^{2}\sqrt{4-x^2}\,dx$ using your calculator and confirm graphically that this is the area between the curve and the $x$-axis.
    \vspace{\stretch{1}}
    
    This even works for constant functions! Remember the train problem from the other day? A train moves along a track at a steady rate of 75 miles per hour from 7 am to 9 am. Express the total distance traveled as an integral. Evaluate the integral.
\end{questions}



\newpage
