\addcontentsline{toc}{subsection}{Modeling \& Optimization}
\subsection*{Modeling \& Optimization}
\begin{questions}
    \question An open-top box is to be made by cutting congruent squares of side length x from the corners of a 20-by-25-inch sheet of tin and bending up the sides.  Find how large the cut-out squares should be so that the box can hold as much as possible.  Find the resulting maximum volume. [1, 7]
    
    \vspace{\stretch{2}}
    
    \question Find the largest possible value of $2x+y$  if x and y are the lengths of the sides of a right triangle whose hypotenuse is $\sqrt{5}$ units long. [2]
    
    \vspace{\stretch{1}}
    
    \newpage
    
    \question Find two positive numbers whose sum is 36 and whose product is as large as possible. [3, 6]
    \vspace{\stretch{1}}

    \question The city recreation department plans to build a rectangular playground having an area of 3600 square meters and surround it by a fence.  Find the dimensions of the rectangle that uses the least amount of fencing.  [4, 8, 11, 16]
    \vspace{\stretch{1}}

    \question Find the radius and height of a right circular cylinder that minimizes total surface area for a volume of $36\pi$ cubic inches.  [5, 9]
    \vspace{\stretch{1}}
    
    \newpage
    
    \question An isosceles triangle has its vertex at the origin and its base parallel to the x-axis with the vertices above the axis on the curve $y=27-x^2$. Find the largest area the triangle can have. [10, 19]
    \vspace{\stretch{1}}
    
    \question A carpenter has been asked to build an open box with a square base.  The sides of the box will cost \$3 per square meter, and the base will cost \$4 per square meter.  Find the dimensions of the box of greatest volume that can be constructed for \$48.  [12,13,14,17]
    \vspace{\stretch{1}}
    
    \question Find the dimensions of the right circular cylinder of greatest volume inscribed in a right circular cone of radius 10 inches and a height of 24 inches.  [15, 18]
    \vspace{\stretch{1}}
    
    
\end{questions}




\newpage
