\addcontentsline{toc}{subsection}{Distance, Velocity, \& Acceleration}
\subsection*{Distance, Velocity, \& Acceleration}
\noindent\textbf{Distance:} The function $s(t)$ gives the position $s$ on a line as a function of time $t$.\\
\noindent\textbf{Displacement:} The displacement of an object over the time interval from $t$ to $t+\Delta t$ is $\Delta s=f(t+\Delta t)-f(t)$.\\
\noindent\textbf{Velocity:} The derivative of the position equation is velocity because it describes how fast the position is changing. $v(t)=s'(t)$
\begin{questions}
    \question Average Velocity: the average velocity over a period of time. $\displaystyle\frac{\Delta s}{\Delta t}$, where $\Delta s$ represents \textbf{displacement} and $\Delta t$ represents the \textbf{time traveled}.
    \vspace{.1cm}
    \question Instantaneous Velocity: how fast \textbf{and in what direction} an object is moving at a given instant.
    \begin{parts}
        \part Velocity is \textbf{positive} when the object is moving forward or up and the distance is increasing.
        \part Velocity is \textbf{negative} when the object is moving back or down and the distance is decreasing.
    \end{parts}
    \question Speed: how fast an object is moving at a given instant, $\displaystyle |v(t)|=\left|\frac{ds}{dt}\right|$. The only difference between velocity and speed is that velocity includes \textbf{direction}.
\end{questions}
\noindent\textbf{Acceleration:} The derivative of the velocity equation is acceleration because it describes \textbf{how fast the velocity is changing}. $\displaystyle a(t)=\frac{dv}{dt}=\frac{d^2 s}{dt^2}$\\
\\
\noindent\textbf{Examples:}\\
For each of the following, $s$ represents the position of a moving body with $s$ in feet and $t$ in seconds. Find the body's velocity and acceleration.
\begin{questions}
    \question $s(t)=16t^2+3$
    \vspace{\stretch{1}}
    \question $s(t)=832t-16t^2$
    \vspace{\stretch{1}}
    
    \newpage
    
    
    \question The position of a body at time $t$ is $s=t^3-4t^2-3t$. Find the acceleration each time the velocity is zero.
    \vspace{\stretch{1}}
    
    \question A particle moves along a line so that its position at any time $t\ge0$ is given by the function $s(t)=t^2-4t+3$, where $s$ is measured in meters and $t$ is measured in seconds.
    \begin{parts}
        \part Find the displacement in the first 2 seconds.
        \part Find the average velocity in the first 4 seconds.
        \part Find the instantaneious velocity when $t=4$.
        \part Find the acceleration when $t=4$.
        Describe the motion of the particle. At what values of $t$ does the particle change direction?
        \part Where is the particle when $s$ is a minimum?
        \vspace{\stretch{1}}
    \end{parts}
    
    \question A ball is thrown vertically upward at a speed of 30 m/s. Its height in meters $t$ seconds later is given by $h(t)=30t-5t^2$.
    \begin{parts}
        \part Find the maximum height of the ball.
        \part Find the acceleration of the ball.
    \end{parts}
    \vspace{\stretch{.80}}
\end{questions}


\newpage
