\addcontentsline{toc}{subsection}{Integral Test \& \textit{p}-Series}
\subsection*{Integral Test \& \textit{p}-Series}
Let's start this section with an example...\\
\\
Consider the series: $\displaystyle\sum_{n=1}^\infty \frac{1}{n^2}=\frac{1}{1^1}+\frac{1}{2^2}+\frac{1}{3^2}+...$\\
\\
First, verify that the Divergence Test is inconclusive and that this is not a geometric series.\\
\vspace{\stretch{1}}


Does the series converge?
\vspace{\stretch{3}}


\newpage

\begin{tcolorbox}[title= THE INTEGRAL TEST,colframe=black,sharp corners,colback=white,colbacktitle=white,coltitle=black]

    If $a_n=f(n)$ and $f$ is continuous, positive, and decreasing on $[1,\infty)$, then
    \[\sum_{n=1}^{\infty}a_n\hspace{.35in}\text{and}\hspace{.35in} \int_1^{\infty}f(x)\,dx\]
    either both converge or diverge.

\end{tcolorbox}
\vspace{.1in}

\noindent\textbf{THREE IMPORTANT FACTS}:
\begin{questions}
    \question They do \textbf{not} converge to the same value! In the example we just did:
    \[\displaystyle\sum_{n=1}^\infty \frac{1}{n^2}=\frac{\pi^2}{6}\ne1=\int_1^\infty\frac{1}{x^2}\,dx\]
    
    \question We can start at other indices (limits of integration).
    
    \question $f$ does not have to be always decreasing, only \textbf{ultimately} decreasing.
\end{questions}
\vspace{.1in}

\noindent\textbf{Examples:} Determine the convergence or divergence of each series.
\begin{parts}
    \part $\displaystyle\sum_{n=1}^{\infty}\frac{n}{n^2+1}$
    \vspace{\stretch{1}}
    
    \part $\displaystyle\sum_{n=1}^{\infty}\frac{5}{2n^2+2}$
    \vspace{\stretch{1}}
    
    \part $\displaystyle\sum_{n=2}^{\infty}\frac{1}{n\ln(n)}$
    \vspace{\stretch{1}}
\end{parts}

\newpage

\begin{tcolorbox}[title= DEFINITION OF A $p$-SERIES,colframe=black,sharp corners,colback=white,colbacktitle=white,coltitle=black]

    A series of the form \[\displaystyle\sum_{n=1}^\infty \frac{1}{n^p}=\frac{1}{1^p}+\frac{1}{2^p}+\frac{1}{3^p}+...\] is a \textbf{\textit{p}-series}, where $p$ is a positive constant. For $p=1$, the series \[\sum_{n=1}^\infty\frac{1}{n}=\frac{1}{1}+\frac{1}{2}+\frac{1}{3}+...\]
    is called the \textbf{harmonic series}. A \textbf{general harmonic series} is of the form $\displaystyle\sum_{n=1}^\infty\frac{1}{an+b}$.

\end{tcolorbox}
\begin{tcolorbox}[title= CONVERGENCE OF A $p$-SERIES,colframe=black,sharp corners,colback=white,colbacktitle=white,coltitle=black]

    A series of the form \[\displaystyle\sum_{n=1}^\infty \frac{1}{n^p}=\frac{1}{1^p}+\frac{1}{2^p}+\frac{1}{3^p}+...\] converges if $p>1$ and diverges if $0<p\le1$.

\end{tcolorbox}
\vspace{.1cm}

\noindent\textbf{Examples:}
\begin{questions}
    \question Determine the convergence or divergence of each series.
    \begin{parts}
        \begin{minipage}{0.23\linewidth}
            \part $\displaystyle\sum_{n=1}^{\infty}\frac{1}{\sqrt{n}}$
        \end{minipage}
        \hfill
        \begin{minipage}{0.23\linewidth}
            \part $\displaystyle\sum_{n=1}^{\infty}\frac{1}{n\sqrt{n}}$
        \end{minipage}
        \hfill
        \begin{minipage}{0.23\linewidth}
            \part $\displaystyle\sum_{n=1}^{\infty}\frac{1}{n^{1.04}}$
        \end{minipage}
        \vspace{\stretch{1}}
    \end{parts}

    \question Find the positive values of $p$ for which the series converges:

    \begin{parts}
        \begin{minipage}{0.45\linewidth}
            \part $\displaystyle\sum_{n=2}^{\infty}\frac{1}{n\left(\ln(n)\right)^p}$
        \end{minipage}
        \hfill
        \begin{minipage}{0.45\linewidth}
            \part $\displaystyle\sum_{n=1}^{\infty}\frac{n}{(1+n^2)^p}$
        \end{minipage}
        \vspace{\stretch{3}}
    \end{parts}

\end{questions}




\newpage
