\addcontentsline{toc}{subsection}{Constant of Integration \& Applications}
\subsection*{Finding the Constant of Integration}

\begin{questions}
    \question Given $f'(x)=4x^5$ and $f(1)=1$, find $f(x)$.
    \vspace{\stretch{1}}
    
    \question Given $f'(x)=(x^2-3x+2)(x-2)$ and $f(-2)=0$, find $f(x)$.
    \vspace{\stretch{1}}
    
    Solve the differential equations subject to the given initial conditions.
    \question $\displaystyle\frac{dy}{dx}=4(x-7)^3,\,y=10$ when $x=8$.
    \vspace{\stretch{1}}
    
    \question The graph of $y$ passes through the point $(4,\,13)$ with slope 5 and $\displaystyle\frac{d^2y}{dx^2}=\frac{3x}{8}$. Find $y$.
    \vspace{\stretch{1}}
\end{questions}

\subsection*{Applications of Integration}
\begin{questions}
    \setcounter{question}{4}
    \question A particle moving on a straight line has acceleration $a(t)=5-3t$ in ft/sec$^2$, and its velocity is 7 ft/sec at 2 seconds. If $s(t)$ is the distance from the origin, find $s(2)-s(1)$.
    
    \vspace{\stretch{.7}}
    
    \newpage
    
    \question A motorist applies the brakes on a car moving at 45 miles per hour on a straight road, and the brakes cause a constant deceleration of 22 ft/sec$^2$. In how many seconds will the car stop, and how many feet will the car have traveled after the time the brakes were applied?
    \vspace{\stretch{1}}
    
    \question Find the equation of a curve such that $y''$ is always 2, and at the point $(2,\,6)$ the slope of the tangent line is 10.
    \vspace{\stretch{1}}
    
    \question A stone is thrown straight up from a building ledge that is 120 feet above the ground with an initial velocity of 96 ft/sec. When will the stone reach its maximum height? What will the maximum height be? When will the stone hit the ground? With what speed will it hit the ground?
    \vspace{\stretch{1}}
    
    
\end{questions}


\newpage
