\addcontentsline{toc}{subsection}{Related Rates}
\subsection*{Related Rates}
\begin{questions}
    \question A snowball is melting at a rate of 2 cubic feet per hour.  If it remains spherical, at what rate is the radius changing when the radius of the snowball is 20 inches?  At what rate is the surface area changing when the radius is 20 inches?  [1, 2, 3]
    \vspace{\stretch{1.7}}
    
    \question A small funnel in the shape of a cone is being emptied of fluid at the rate of 12 cubic centimeters per second.  The height of the funnel is 20 centimeters and the radius of the top is 4 centimeters.  How fast is the fluid level dropping when the level stands 5 centimeters above the vertex?  [4, 5]
    \vspace{\stretch{1}}
    
    \newpage
    
    \question Sand is poured on a conical pile at a rate of 20 cubic meters per minute.  The height of the pile is always equal to the radius of the base of the pile.  When the pile is 3 meters high, how fast is the height of the pile increasing?  [6]
    \vspace{\stretch{1}}
    
    You can now complete [14, 16, 18, 20, 22, 24, and 25]
    \question A ladder leans against a vertical wall with the bottom of the ladder 8 feet from the wall on a horizontal floor.  At that time, the bottom end of the ladder is being pulled away at the rate of 3 ft/sec and the top of the ladder slips down the wall at the rate of 4 ft/sec.  How long is the ladder?  [7, 8, 9, 10, 15, 17, 19, 21, 23]
    \vspace{\stretch{1}}
    
    \question An object moves on a parabola $3y=x^2$. When $x = 3$, the $x$-coordinate of the object is increasing at the rate of 1 foot per minute.  How fast is the $y$-coordinate increasing at that moment?  [11, 12]
    \vspace{\stretch{1}}
    
    \newpage
    
    \question A balloon rises vertically at the rate of 5 ft/sec.  A person on the ground 200 feet away from the spot below the rising balloon watches the balloon ascend.  At what rate is the distance between the balloon and the observer changing when the balloon is 50 feet above the ground? \textbf{Don’t confuse this problem with the following one!}
    
    \vspace{\stretch{1}}
    
    \question A balloon rises vertically at the rate of 10 feet per second.  A person watches the balloon ascend from a point on the ground that is 100 feet away from the spot below the rising balloon.  At what rate (radian/second) is the observer’s head rotating upward to follow the balloon when the balloon is 50 feet above the level of the observer’s head?  [13]
    \vspace{\stretch{1}}
    
    \question A man 6 feet tall walks at a rate of 5 ft/sec toward a street light that is 16 feet above the ground.  At what rate is the tip of his shadow moving?  At what rate is the length of his shadow changing when he is 10 feet from the base of the light? [26, 27]
    
    \vspace{\stretch{1}}
    
    
\end{questions}






\newpage
