\addcontentsline{toc}{subsection}{Logistic Differential Equations}
\subsection*{Logistic Differential Equations}

Before we talk about the LDE, first let's consider the following scenario:
\begin{questions}
    \question Let $N(t)$ be the population of wild coyotes in observed in a study of a wildlife reserve, with $t$ in years. The growth of the population is proportional to $650-N$. Initially, there are 300 coyotes. After two years, there is observed to be 500 coyotes. Find $N(3)$.
    
    \vspace{\stretch{1.2}}
\end{questions}

Correct answer! However, there is something \textit{inaccurate} about our work. What is it? Why?



\begin{center}
    \underline{A 'Normal' Differential Equation}
\end{center}
\begin{minipage}{0.45\linewidth}
    
        Differential Equation: $\displaystyle\frac{dy}{dt}=ky$
    
\end{minipage}
\hfill
\begin{minipage}{0.45\linewidth}
    
        General Solution: $\displaystyle y=Ce^{kt}$
    
\end{minipage}

This type of differential equation allows for \textbf{unlimited growth}. Obviously, we do not live in a world of infinites, so there cannot be an infinite number of coyotes as time goes on. We need a \textbf{carrying capacity}, $L$, to limit our growth. 


\begin{center}
    \underline{The Logistic Differential Equation}
\end{center}
\begin{minipage}{0.45\linewidth}
    
        Differential Equation:\\ 
        $\displaystyle\frac{dy}{dt}=ky\left(1-\frac{y}{L}\right)$ or $\displaystyle\frac{dy}{dt}=\frac{ky}{L}(L-y)$

\end{minipage}
\hfill
\begin{minipage}{0.45\linewidth}
    
        General Solution: $\displaystyle y=\frac{L}{Ce^{-kt}+1}$
    
\end{minipage}

\vspace{.25in}

%typo

\begin{center}
    \textbf{\large Memorize both forms of the differential equation and its general solution for the BC Exam!}
\end{center}


\newpage



\begin{questions}
    \setcounter{question}{1}
    \question 40 elk are released into a game refuge. After 5 years, the population of elk is observed to be 104. The game warden says that the refuge can support no more than 4000 elk at any given time.
    \begin{parts}
        \part Write a differential equation for the population of elk.
        \vspace{\stretch{1}}
        
        \part Write a model for the population, $P$, in terms of $t$. (Use the general solution, do not attempt to integrate!)
        \vspace{\stretch{1}}
    \end{parts}
    
    \question Find $\displaystyle\frac{d^2 y}{dx^2}$ for the general L.D.E. What can we deduce based on this function?
    \vspace{\stretch{1}}
\end{questions}


\textit{\footnotesize Solving for the general solution to a LDE requires an integration method not yet covered. We will circle back and derive it as an exercise later.}


\newpage
