\addcontentsline{toc}{subsection}{Differentials, Linearization, Newton's Method}
\subsection*{Differentials}
\begin{tcolorbox}[title= DEFINITION OF A DIFFERENTIAL,colframe=black,sharp corners,colback=white,colbacktitle=white,coltitle=black,boxrule=1pt]

    Let $y=f(x)$ be a differentiable function. The differential $dx$ is an independent variable. The differential $dy$ is $dy=f'(x)\,dx$.
    
\end{tcolorbox}
\noindent\textbf{Examples:} Find the differential $dy$ and evaluate $dy$ for the given values of $x$ and $dx$.
\begin{questions}
    \question $y=x^5+37x,\,x=1,\,dx=0.01$
    \vspace{\stretch{.8}}
    
    \question $y=\sin3x,\,x=\pi,\,dx=-0.02$
    \vspace{\stretch{.8}}
    
    \question $x+y=xy,\,x=2,\,dx=0.05$
    \vspace{\stretch{.8}}
\end{questions}

We can use differentials to estimate the change in the value of a function! Let $f(x)$ be differentiable at $x=a$. The approximate change in the value of $f(x)$ when $x$ changes from $a$ to $a+dx$ is $df=f'(a)\,dx$.
\begin{questions}
    \setcounter{question}{3}
    \question The radius of a circle is to be increased from $r=10$ to $r=10.1$. Use differentials to estimate the change in area. Calculate the estimated percent change.
    \vspace{\stretch{1.2}}
\end{questions}

\subsection*{Linearization \& Newton's Method}
This section has been replaced with a small take-home assignment. Expect to see this material on a quiz of test. It is not dense enough to merit the use of in-class instruction. Come find me outside of class if you have questions.

\begin{center}
    Link to File:
    
    \vspace{.2cm}
    
    \qrcode{https://drive.google.com/file/d/1GqxwEAv6EcMuU0GQZDaL8cGVEBIjYr5e/view?usp=sharing}
    
\end{center}



\newpage
